FraCaS: 80 percent complete

### 2019-01-18 paper2018/paper.tex
error analysis

\todo{error analysis}

>>>>

\paragraph{error analysis}
Our system fails to classify correctly 28 problems of of 259 attempts.
Unfortunately, it isn't easy to concisely characterize the areas where
it fails.  The biggest source of error can be attributed to its
incorrect handling of groups
(013,014,046,084,111,124,126,127,137,171,172,191,193,195,243,250,333,346). These
are cases where a conjunction of individuals is treated as group, or
where counting members of a group is necessary.  Other notable
problematic cases are that definite plural does not have universal
reading are incorrectly classified (091,094,095). Neither measure
phrases (242) nor attributive comparatives (244,245) are handled.
